Total Platform Cyber Protection

### 2016-06-11 paper.tex
Section 8.2.6 is completed

\subsubsection{Protection against malicious code}

>>>>

\subsubsection{Protection against malicious code}
One of the challenging areas of application security is allowing arbitrary code execution without having to compromise security. There are situations in which applications need to run user provided code, reuse codes that were written in a non-type-safe language or host another program. For instance, browsers running web applications or apps being uploaded to app stores. In order to run codes safely and making sure that they are not executing malicious code, there are number of protection mechanisms that can be used, one of which is Sandboxing. it is also known as Software Fault Isolation (SFI)~\cite{Wahbe1993}. The idea is to run the code in an isolated environment within the applications address space called fault domain and then prevent the code from accessing outside of that fault domain.

Early research is focused on rewriting unsafe instructions and providing interface for system calls to restrict program's access~\cite{Wahbe1993,Mccamant2006}. Native Client (NaCl)~\cite{Yee2009a} is a sandbox provided by Google that offers x86 untrusted Native code execution in Chrome browser using x86 memory segmentation. Therefore, web developers can leverage the performance of executing native code in a safe environment. Xax~\cite{Douceur2008} is another similar technology that is in form of a browser plug-in that provides an abstraction layer for OS system calls. Other research extends this technology by covering ARM and x86-64~\cite{Zhao2011, Sehr2010,Ansel}. Others attempt to reduce the overhead of performing binary rewriting and memory isolation~\cite{Ford2008,Jana2011}. Sandboxing is also used for executing untrusted native code in Android applications~\cite{Sun2014,Afonso2016}.

The other approach towards protecting against malicious code is to analyze the code and detect malicious behavior~\cite{Zhou2012}. Despite all the efforts that have been made to keep malicious apps off the Android market, malicious apps can still find their way into the app store by bypassing the Google Bouncer~\cite{Lockheimer:2012} using different techniques. Bouncer uses sandboxing techniques to run apps in a confined environment, but researchers~\cite{oberheide2012dissecting} have shown that apps can fingerprint Bouncer and the environment in which they are being analyzed, using evasion and obfuscating techniques to complicate the reverse engineering process. If apps could detect that they are being analyzed, they can hold off on running their malicious code while being analyzed. A lot of research has been done to fingerprint the Android analyzers to show that evading detection is possible~\cite{Maier2014,Jing2014,Vidas2014}. Other approaches are using analysis to detect logic bombs, that is, when an application changes its behavior under certain conditions~\cite{Fratantonio2016}.
